\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-27 Report/project_report.tex

\begin{equation}
\delta\mbf{x} := \bbm \delta \mbf x_0 \\ \vdots \\ \delta \mbf x_K \\ \delta \mbf f_1 \\ \vdots \\ \delta \mbf f_N\ebm,
\end{equation}
where $N$ is the number of unique features observed in the window and 
\begin{equation}
\mathbf{H} := \begin{bmatrix}
 -\mbf H_{\mbf x, 1} & \mbf 1 & &  & &   \\ 
 & -\mbf G_{\mbf x, 1} &  &  &  &   -\mbf G_{\mbf f, 1} \\ \hline
 & -\mbf H_{\mbf x, 2} & \mbf 1 & & &    \\ 
 & & -\mbf G_{\mbf x, 2} &  & &  -\mbf G_{\mbf f, 2}   \\ \hline
 &  & \ddots & \ddots & & \vdots  \\  \hline
  & & & -\mbf H_{\mbf x, K} & \mbf 1 & \\ 
 & & & & -\mbf G_{\mbf x, K} &  -\mbf G_{\mbf f, K}   \\  
\end{bmatrix}, 
\end{equation},

@@

\subsection{MSCKF State Parametrization}
We evaluated the MSCKF using a dataset in which the IMU `measures' gravity-corrected linear velocities rather than raw linear accelerations (see Section \ref{sec:experiments}).
In order to accommodate this alternative state parametrization, the mathematical framework described in this section differs slightly from that described in \cite{Mourikis:2007:ICRA}.

>>>>

\begin{equation}
\delta\mbf{x} := \bbm \delta \mbf x_0 \\ \vdots \\ \delta \mbf x_K \\ \delta \mbf f_1 \\ \vdots \\ \delta \mbf f_N\ebm,
\end{equation}
where $N$ is the number of unique features observed in the window and 
\begin{equation}
\mathbf{H} := \left[\begin{array}{cccccc}
 -\mbf H_{\mbf x, 1} & \mbf 1 & &  & &   \\ 
 & -\mbf G_{\mbf x, 1} &  &  &  &   -\mbf G_{\mbf f, 1} \\ \hline
 & -\mbf H_{\mbf x, 2} & \mbf 1 & & &    \\ 
 & & -\mbf G_{\mbf x, 2} &  & &  -\mbf G_{\mbf f, 2}   \\ \hline
 &  & \ddots & \ddots & & \vdots  \\  \hline
  & & & -\mbf H_{\mbf x, K} & \mbf 1 & \\ 
 & & & & -\mbf G_{\mbf x, K} &  -\mbf G_{\mbf f, K}   \\  
\end{array}\right], 
\end{equation},

@@

\subsection{MSCKF State Parametrization}
We evaluated the MSCKF using a dataset in which the IMU `measures' gravity-corrected linear velocities rather than raw linear accelerations (see Section \ref{sec:experiments}).
In order to accommodate this alternative sensor configuration, the mathematical framework described in this section differs slightly from that described in \cite{Mourikis:2007:ICRA}.
